Simulating the Linux page cache in distributed applications with WRENCH

### 2020-12-10 paper_io_sim.tex
replaced tabs with spaces
Small edits

            We also implemented our model in WRENCH, separately from existing WRENCH components. 
            We exposed page cache simulation through a user API, activated using a command-line argument.
            We used SimGrid 3.25 which is available at \url{https://framagit.org/simgrid/simgrid}.
            To implement the simulator, we used the WRENCH 1.6 version at this commit \url{https://github.com/wrench-project/wrench/tree/67185374330d2c4bf274fce222c937e838df5b03}.

@@

        To parametrize our simulators, we benchmarked the bandwidths of
        memory, local disk, remote disk (NFS), and network
        (Table~\ref{table:benchmark}). Since WRENCH currently only supports
        symmetrical bandwidths, we use the mean of the read and write
        bandwidth values in our experiments.
            \begin{table}[htbp]
            \centering
            \begin{tabularx}{\columnwidth}{|l
            |>{\centering\arraybackslash}X
            |>{\centering\arraybackslash}X
            |>{\centering\arraybackslash}X|}
            \hline
                Bandwidths  & Cluster (real) & Python simulator & WRENCH simulator\\
            \hline
                Memory read  & 6860    & 4812     & 4812\\
                Memory write & 2764    & 4812 & 4812\\
                Local disk read & 510 & 465 & 465\\
                Local disk write & 420 & 465     & 465\\
                Remote disk read & 515 & - & 445\\
                Remote disk write & 375 & - & 445\\
                Network & 3000 & - & 3000\\
            \hline
            \end{tabularx}
            \caption{Bandwidth benchmarks (MBps) and simulator configurations.
            The bandwidths used in the simulations are the average of the read and write bandwidths
            measured in the cluster.
            Remote disk and network accesses are not simulated in the Python simulator. \tristan{table could be prettified}}
            \label{table:benchmark}
            \end{table}

>>>>

            We also implemented our model as part of WRENCH, enhancing its internal implementation
            and APIs with a page cache abstraction, acticated on-demand via a {\tt --pagecache}
            command-line argument. For the experiments in this paper we use WRENCH 1.6 at this commit \url{https://github.com/wrench-project/wrench/tree/67185374330d2c4bf274fce222c937e838df5b03}, which uses
            SimGrid 3.25 (available at \url{https://framagit.org/simgrid/simgrid}). However, our implementation is now part of WRENCH's master branch and will be available to users with the next WRENCH release.

@@

        To parametrize our simulators, we benchmarked the bandwidths of
        memory, local disk, remote disk (NFS), and network
        (Table~\ref{table:benchmark}). Since SimGrid, and thus WRENCH, currently only supports
        symmetrical bandwidths, we use the mean of the read and write
        bandwidth values in our experiments.
            \begin{table}[htbp]
            \centering
            \begin{tabularx}{\columnwidth}{|l
            |>{\centering\arraybackslash}X
            |>{\centering\arraybackslash}X
            |>{\centering\arraybackslash}X|}
            \hline
                Bandwidths  & Cluster (real) & Python simulator & WRENCH simulator\\
            \hline
                Memory read  & 6860    & 4812     & 4812\\
                Memory write & 2764    & 4812 & 4812\\
                Local disk read & 510 & 465 & 465\\
                Local disk write & 420 & 465     & 465\\
                Remote disk read & 515 & - & 445\\
                Remote disk write & 375 & - & 445\\
                Network & 3000 & - & 3000\\
            \hline
            \end{tabularx}
            \caption{Bandwidth benchmarks (MBps) and simulator configurations.
            The bandwidths used in the simulations are the average of the read and write bandwidths
            measured in the cluster.
            Remote disk and network accesses are not simulated in the Python simulator. \tristan{table could be prettified}}
            \label{table:benchmark}
            \end{table}
